Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-12-18 aa workingdraft/draft.tex

sediment traps were installed immediately before each run, then a slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes). Channel velocity was kept at 6 cm/s for this period across $\Rey_c$ treatments, then adjusted to the appropriate value for the treatment. This procedure was intended to make particle concentration longitudinally even throughout the system. Estimated depth-averaged starting concentration was 82.3 mg/L (\SI{53.8}{\micro\liter/\liter}).

@@

\subsection{Turbulence and Flow Characteristics}

@@

The ECE we observed at our lowest $\Rey_c$ and collector-density treatment (1.92\%) is one of the highest observed in any previous laboratory experiment with multiple collectors \cite{stein2020}. Our observation did fall above the value (1.67\%) predicted by the Fauria et al. model \cite{Fauria_2015} that was fit at that collector density . However, the anomalous result that also influenced that model's fit (Figure \ref{fig:compplot}) probably explains some or all of that difference. On the whole, our results demonstrate that the Fauria et al. model remains a reasonably good predictor of ECE even at collector densities far lower than those they studied.

@@

The presence of biofilm was found to have a substantial positive effect on ECE. Because Fauria et al. \cite{Fauria_2015} already confirmed that the negative effect of $\Rey_c$ on ECE is supported both with and without biofilm present, and because the duration of growth makes biofilm runs quite time-intensive, we focused solely on collector density's interactions with biofilm. Roughly equivalent biofilm growth (visibly apparent after 13-20 days) resulted in fairly similar relative increase of ECE across our collector density parameter range (improvement to 1.53--2.38 times control), despite quite different absolute values of ECE. As Fauria et al. \cite{Fauria_2015} found for $\Rey_c$, biofilm-positive runs exhibited a consistent negative relationship between collector density and ECE.

Absolute effects of biofilm were on par with those of $\Rey_c$ and collector density across our parameter space. At the Reynolds number (200) used for biofilm experiments, ECE ranged from 0.10\% to 0.48\% across our collector-density treatments without biofilm, for an effect size of 0.38\%, and absolute effects of biofilm ranged from +0.07\% ECE to +0.71\% ECE. Differences in ECE across varying $\Rey_c$ (0.20\%--1.71\% ECE) were larger than the biofilm effect sizes by a ratio of roughly 2.5:1. This demonstrates biofilm's effect is on the same order of magnitude as the other variables, but the fact that our parameter ranges span an arbitrary fraction of possible natural values mean that these comparisons should be considered to be inexact.

>>>>

Sediment traps were installed immediately before each run, then a slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes). Channel velocity was kept at 6 cm/s for this period across $\Rey_c$ treatments, then adjusted to the appropriate value for the treatment. This procedure was intended to make particle concentration longitudinally even throughout the system. Estimated depth-averaged starting concentration was 82.3 mg/L (\SI{53.8}{\micro\liter/\liter}).

@@

\subsection{Turbulence}

@@

The ECE we observed at our lowest $\Rey_c$ and collector-density treatment (1.92\%) is one of the highest observed in any previous laboratory experiment with multiple collectors \cite{stein2020}. Our observation did fall above the value (1.67\%) predicted by the Fauria et al. model \cite{Fauria_2015} that was fit at that collector density. However, the anomalous experiment at the middle $\Rey_c$ treatment that also influenced that model's fit (Figure \ref{fig:compplot}) probably explains some or all of that difference. Removing this anomaly would leave only two points, overfitting the model by definition, so we chose to leave it in as a lesser of two evils. On the whole, our results demonstrate that the Fauria et al. model remains a reasonably good predictor of ECE even at collector densities far lower than those they studied.

@@

The presence of biofilm was found to have a substantial positive effect on ECE. Because Fauria et al. \cite{Fauria_2015} already confirmed that the negative effect of $\Rey_c$ on ECE is supported both with and without biofilm present, and because the duration of growth makes biofilm runs quite time-intensive, we focused solely on collector density's interactions with biofilm. Roughly equivalent biofilm growth (visibly apparent after 13-20 days) resulted in fairly similar relative increase of ECE across our collector density parameter range (improvement to 1.53--2.38 times control), despite quite different absolute values of ECE. As Fauria et al. \cite{Fauria_2015} found for $\Rey_c$, biofilm-positive runs exhibited consistent decline in ECE with increasing collector density.

Absolute effects of biofilm were on par with those of $\Rey_c$ and collector density across our parameter space. At the Reynolds number (200) used for biofilm experiments, ECE ranged from 0.10\% to 0.48\% across our collector-density treatments without biofilm, for an effect size of 0.38\%, and absolute effects of biofilm ranged from +0.07\% ECE to +0.71\% ECE. Absolute effects of $\Rey_c$ (0.20\%--1.71\% ECE) on ECE for specific collector densities were larger than the biofilm effect sizes by a ratio of roughly 2.5:1. This demonstrates biofilm's effect is on the same order of magnitude as the other variables, but the fact that our parameter ranges span an arbitrary fraction of possible natural values means that these comparisons should be considered to be inexact.
